objective function with the penalty term

### 2017-06-20 analysis/Objcheck_2.Rmd
Files commited by wflow_commit.

sim_rank0 = function(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1,mtype = "fdr"){
  T = 200
  RMSE = rep(NA,T)
  sign_obj = rep(NA,T)
  for(t in 1:T){
    g0 = rank0check(K = 1,N, P, SF, SL , signal,noise,mtype = mtype)
    RMSE[t] = g0$rmse
    sign_obj[t] = sign(g0$obj_val - g0$obj_0)
  }
  par(mfrow = c(2, 2))
  par(cex = 0.6)
  par(mar = c(3, 3, 0.8, 0.8), oma = c(1, 1, 1, 1))
  boxplot(RMSE,main = "RMSE")
  hist(sign_obj, breaks = 3,main = "sign of difference of obj value")
  hist(RMSE,breaks = 50,main = "RMSE")
  plot(sign_obj,RMSE, main = "sign of obj diff vs RMSE")
}

@@

sim_rank0_old = function(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1,mtype = "shrink"){
  T = 200
  RMSE = rep(NA,T)
  sign_obj = rep(NA,T)
  for(t in 1:T){
    g0 = rank0check_old(K = 1,N, P, SF, SL , signal,noise,mtype = mtype)
    RMSE[t] = g0$rmse
    sign_obj[t] = sign(g0$obj_val - g0$obj_0)
  }
  par(mfrow = c(2, 2))
  par(cex = 0.6)
  par(mar = c(3, 3, 0.8, 0.8), oma = c(1, 1, 1, 1))
  boxplot(RMSE,main = "RMSE")
  hist(sign_obj, breaks = 3,main = "sign of difference of obj value")
  hist(RMSE,breaks = 50,main = "RMSE")
  plot(sign_obj,RMSE, main = "sign of obj diff vs RMSE")
}
```

>>>>

sim_rank0 = function(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1,mtype = "fdr"){
  T = 200
  RMSE = rep(NA,T)
  diff_obj = rep(NA,T)
  for(t in 1:T){
    g0 = rank0check(K = 1,N, P, SF, SL , signal,noise,mtype = mtype)
    RMSE[t] = g0$rmse
    diff_obj[t] = (g0$obj_val - g0$obj_0)
  }
  par(mfrow = c(2, 2))
  par(cex = 0.6)
  par(mar = c(3, 3, 0.8, 0.8), oma = c(1, 1, 1, 1))
  boxplot(RMSE,main = "RMSE")
  hist(diff_obj, breaks = 3,main = "sign of difference of obj value")
  hist(RMSE,breaks = 50,main = "RMSE")
  plot(diff_obj,RMSE, main = "sign of obj diff vs RMSE")
  return(c(sum(diff_obj == 0),sum(diff_obj>0),diff_obj<0)/T)
}

@@

sim_rank0_old = function(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1,mtype = "shrink"){
  T = 200
  RMSE = rep(NA,T)
  diff_obj = rep(NA,T)
  for(t in 1:T){
    g0 = rank0check_old(K = 1,N, P, SF, SL , signal,noise,mtype = mtype)
    RMSE[t] = g0$rmse
    diff_obj[t] = (g0$obj_val - g0$obj_0)
  }
  par(mfrow = c(2, 2))
  par(cex = 0.6)
  par(mar = c(3, 3, 0.8, 0.8), oma = c(1, 1, 1, 1))
  boxplot(RMSE,main = "RMSE")
  hist(diff_obj, breaks = 3,main = "sign of difference of obj value")
  hist(RMSE,breaks = 50,main = "RMSE")
  plot(diff_obj,RMSE, main = "sign of obj diff vs RMSE")
  return(c(sum(diff_obj == 0),sum(diff_obj>0),diff_obj<0)/T)
}
```
